Visualising Life Satisfaction in Countries across Europe: Individual- and Multi-Level Evidence on Cultural and Pecuniary Factors

### 2019-01-31 LaTex/Paper_fulltext.tex

	%% If you have bibdatabase file and want bibtex to generate the bibitems, please use
	\newpage
	\bibliographystyle{elsarticle-harv} 
	\bibliography{Literature}

\end{document}

>>>>

\subsection{The Wider Interplay of Work-Related Variables with Life Satisfaction}
Our analysis features a myriad of variables that can be examined with regard to their effect on overall life satisfaction.
In order to justify our variable selection the following remarks elucidate the respective variables' interplay with life satisfaction.
In contrast to the previous examination of the overall concept of SWB, to accounts on the different variables are presented 
in a briefer manner. Rather than covering the entire theoretical background, the following elaboration is though to spur interest
and curiosity to examine the relation of life satisfaction and other factors on one's own - aided by our interactive 
European Happiness Observer interface.

\subsubsection{Life satisfaction and income}
The life satisfaction-income discussion almost always refers back to \citet{easterlin_does_1974} whose observations regarding
the relation of life satisfaction i.e., happiness and income were dubbed the `Easterlin Paradox'. Indeed, his findings from time series data
suggest that life satisfaction remains flat, despite increases in GDP per capita. These findings still heavily inform other researchers'
work and indicate that the relative income in comparision to others might influence SWB \citep{di_tella_happiness_2010,drichoutis_reference_2010,pedersen_happiness_2011}.
Emphasising relative position follows the lead of behavioural labour economics that builds on the findings of prospect theory \citep{kahneman_prospect_1979}.
This concept implies that reference points rather than absolute positions inform people's choices. In the course of behavioural
labour economics, this backgroundis highly relevant \citep{dohmen_behavioral_2014}. 
While investigations examining relative status and changes over time appear highly relevant and theoretically justified, the present
project ist not suited to cover these questions. Not being in posession of either time series or relative income data, we need
to focus on absolute income at a certain point in time. Although this independent variable might not capture the underlying relation
of income and life satisfaction, it qualifies as a basic means of inquiry that sheds light on the distinction between life satisfaction
and happiness: “high income buys life satisfaction but not happiness.” \citep[p. 16489]{kahneman_high_2010}.

\subsubsection{Pecuniary vs. non-pecuniary factors}
Income-related investigations also stimulate inquiries examining the opposite of monetary factors, namely non-pecuniary
variables. \textit{Since high income might not be all to strive for, which `softer' factors determine a satisfactory life?}
In general, health takes centre-stage as a determinant of life satisfaction. This statement is not only backed by common 
sense or daily wisdom (Who has not said or been told that health is life's most precious gift?) but also by empirical observations \citep{pedersen_happiness_2011}. \\
at the work place and terms like `work-life-balance' and `Generation Y' imply changing perceptions of a pleasant working environment. Also \citet{andersson_happiness_2008}
investigates the special relation between self-employment and life satisfaction with ample regard to health issues. \\
Self-employment as such exhibits a variable that is thought to affect life satisfaction \citep{andersson_happiness_2008,schneck_why_2014,van_der_zwan_self-employment_2018}
due to non-pecuniary circumstances that are innate and to the status of self-employment. \\
This remark also leads to a greater discussion of features proposed by self-determinantion theory \citep{deci_intrinsic_1985,deci_self-determination_1989,ryan_self-determination_2000}.
Lastly, \citet{luo_essays_2018} uses EVS data estimate the effects of pecuniary and non-pecuniary factors on life satisfaction
The EVS, for example, captures to which degree respondents feel the need for a job that enables employees to develop their talents. \\
of the unemployed. Intuitively, financial uncertainty might appear as the major concern of unemployment but further investigations
show the significant role that social and psychological factors play. This observation can be interpreted as a general plea for research on
the interplay of non-pecuniary factors of the work environment and life satisfaction.

\subsubsection{Non-pecuniary factors of the work environment}
Drawing on the previous remarks regarding in incorporation of work-related non-pecuniary variables, our analysis comprises of
multiple factors that touch on leadership responsibilities, self-determination related factors, or the occupation's reputation.
The following variables can be examined using the European Happiness Observer:
\begin{itemize}
   \item Work importance in life
   \item Freedem of job decisions
   \item Job development
   \item Work duty to society
   \item Work should come always first
   \item Supervising responsibilities 
   \item Status of employment (i.e., being self-employed)
   \item International Socio-Economic Index of Occupational Status   
\end{itemize}
%% If you have bibdatabase file and want bibtex to generate the bibitems, please use
\bibliographystyle{elsarticle-harv} 
\bibliography{Literature}
In the working environment, health is not a trivial factor either. The \citet{who_global_1994} stresses the importance of health
\end{document}
